---
title: "iris数据集的分类建模"
author:
  - 牛津徽 SA20008048
documentclass: ctexart
geometry: "left=2.5cm,right=2cm,top=3cm,bottom=2.5cm"
keywords:
  - 中文
  - R Markdown
output:
  rticles::ctex:
    fig_caption: yes
    number_sections: yes
    toc: yes
---
\newpage
# Get Iris from R


```{r, message = FALSE}
library(caret)
library(rattle)
data(iris)
dim(iris)
str(iris)
levels(iris$Species)
head(iris)
a <- subset(iris,Species%in%c("versicolor","virginica"))
#choose versicolor and virginica
a <- droplevels(a)
```

\newpage 
# Create Training  and Testing Sets

```{r}
set.seed(42)
inTrain<-createDataPartition(y=a$Species, p=0.70, list=FALSE)
training.Iris<-a[inTrain,]
testing.Iris<-a[-inTrain,]
```

# Display a pairs plot for the selected variables. 

```{r,warning = FALSE, message = FALSE}
training.Iris %>%
  dplyr::mutate(Species=as.factor(Species)) %>%
  GGally::ggpairs(columns=c(1,2,3,4,5),
                  mapping=ggplot2::aes(colour=Species, alpha=0.5),
                  diag=list(continuous="density",
                            discrete="bar"),
                  upper=list(continuous="cor",
                             combo="box",
                             discrete="ratio"),
                  lower=list(continuous="points",
                             combo="denstrip",
                             discrete="facetbar")) +
  ggplot2::theme(panel.grid.major=ggplot2::element_blank())
```
\newpage 

# preProcess, center and scale the data

```{r}

#training set
preObj<-preProcess(training.Iris[,-5], method = c("center", "scale"))
preObjData<-predict(preObj,training.Iris[,-5])
boxplot(preObjData, main="Normalized data" )
training.Iris_N <- transform(preObjData,Species=training.Iris$Species)
#testing set
preObj<-preProcess(testing.Iris[,-5], method = c("center", "scale"))
preObjData<-predict(preObj,testing.Iris[,-5])
boxplot(preObjData, main="Normalized data" )
testing.Iris_N <- transform(preObjData,Species=testing.Iris$Species)
```

\newpage

# Decision Tree 

```{r}
## The 'rpart' package provides the 'rpart' function.

library(rpart, quietly=TRUE)

## Reset the random number seed to obtain the same results each time.

set.seed(42)
```

## Build the Decision Tree model.

```{r}
rpart <- rpart(Species ~ .,
                   training.Iris_N,
                   method="class",
                   parms=list(split="information"),
                   control=rpart.control(usesurrogate=0, 
                                         maxsurrogate=0),
                   model=TRUE)

## Generate a textual view of the Decision Tree model.

print(rpart)

```
\newpage
## Evaluate model performance on the testing dataset. 

### Generate an Error Matrix for the Decision Tree model.

```{r}
#### Obtain the response from the Decision Tree model.

pr_rpart <- predict(rpart, newdata=testing.Iris_N,
                  type="class")

#### Generate the confusion matrix showing counts.

rattle::errorMatrix(testing.Iris_N$Species, pr_rpart, count=TRUE)

#### Generate the confusion matrix showing proportions.

(per_rpart <- rattle::errorMatrix(testing.Iris_N$Species, pr_rpart))

#### Calculate the overall error percentage.

cat("Calculate the overall error percentage:", 
    100-sum(diag(per_rpart), na.rm=TRUE))

#### Calculate the averaged class error percentage.

cat("Calculate the averaged class error percentage:", 
    mean(per_rpart[,"Error"], na.rm=TRUE))

```
\newpage
### ROC Curve: requires the ROCR package.

```{r}
library(ROCR)

#### ROC Curve: requires the ggplot2 package.

library(ggplot2, quietly=TRUE)

#### Generate an ROC Curve for the rpart model on a [test].

pr_rpart_roc <- predict(rpart, newdata=testing.Iris_N)[,2]

#### Remove observations with missing target.

no.miss   <- na.omit(testing.Iris_N$Species)
miss.list <- attr(no.miss, "na.action")
attributes(no.miss) <- NULL

if (length(miss.list))
{
  pred <- prediction(pr_rpart_roc[-miss.list], no.miss)
} else
{
  pred <- prediction(pr_rpart_roc, no.miss)
}

pe <- performance(pred, "tpr", "fpr")
au <- performance(pred, "auc")@y.values[[1]]
pd <- data.frame(fpr=unlist(pe@x.values), tpr=unlist(pe@y.values))
p <- ggplot(pd, aes(x=fpr, y=tpr))
p <- p + geom_line(colour="red")
p <- p + xlab("False Positive Rate") + ylab("True Positive Rate")
p <- p + ggtitle("ROC Curve Decision Tree a [test] Species")
p <- p + theme(plot.title=element_text(size=10))
p <- p + geom_line(data=data.frame(), aes(x=c(0,1), y=c(0,1)), colour="grey")
p <- p + annotate("text", x=0.50, y=0.00, hjust=0, vjust=0, size=5,
                  label=paste("AUC =", round(au, 2)))
print(p)

#### Calculate the area under the curve for the plot.

no.miss   <- na.omit(testing.Iris_N$Species)
miss.list <- attr(no.miss, "na.action")
attributes(no.miss) <- NULL

if (length(miss.list))
{
  pred <- prediction(pr_rpart_roc[-miss.list], no.miss)
} else
{
  pred <- prediction(pr_rpart_roc, no.miss)
}
performance(pred, "auc")
```
\newpage
# Support vector machine. 

```{r, message = FALSE}
## The 'kernlab' package provides the 'ksvm' function.

library(kernlab, quietly=TRUE)
```


## Build a Support Vector Machine model.

```{r}

set.seed(42)
ksvm <- ksvm(as.factor(Species) ~ .,
                 data=training.Iris_N,
                 kernel="rbfdot",
                 prob.model=TRUE)

## Generate a textual view of the SVM model.

ksvm
```
\newpage
## Evaluate model performance on the testing dataset. 

### Generate an Error Matrix for the SVM model.

```{r}

#### Obtain the response from the SVM model.

pr_ksvm <- kernlab::predict(ksvm, newdata=na.omit(testing.Iris_N))

#### Generate the confusion matrix showing counts.

rattle::errorMatrix(na.omit(testing.Iris_N)$Species, pr_ksvm, count=TRUE)

#### Generate the confusion matrix showing proportions.

(per_ksvm <- rattle::errorMatrix(na.omit(testing.Iris_N)$Species, pr_ksvm))

#### Calculate the overall error percentage.

cat("Calculate the overall error percentage:", 
    100-sum(diag(per_ksvm), na.rm=TRUE))

#### Calculate the averaged class error percentage.

cat("Calculate the averaged class error percentage:", 
    mean(per_ksvm[,"Error"], na.rm=TRUE))
```
\newpage
### ROC Curve: requires the ROCR package.

```{r}
library(ROCR)

#### ROC Curve: requires the ggplot2 package.

library(ggplot2, quietly=TRUE)

#### Generate an ROC Curve for the ksvm model on a [test].

pr_ksvm_roc <- kernlab::predict(ksvm, newdata=na.omit(testing.Iris_N),
                           type    = "probabilities")[,2]

#### Remove observations with missing target.

no.miss   <- na.omit(na.omit(testing.Iris_N)$Species)
miss.list <- attr(no.miss, "na.action")
attributes(no.miss) <- NULL

if (length(miss.list))
{
  pred <- prediction(pr_ksvm_roc[-miss.list], no.miss)
} else
{
  pred <- prediction(pr_ksvm_roc, no.miss)
}

pe <- performance(pred, "tpr", "fpr")
au <- performance(pred, "auc")@y.values[[1]]
pd <- data.frame(fpr=unlist(pe@x.values), tpr=unlist(pe@y.values))
p <- ggplot(pd, aes(x=fpr, y=tpr))
p <- p + geom_line(colour="red")
p <- p + xlab("False Positive Rate") + ylab("True Positive Rate")
p <- p + ggtitle("ROC Curve SVM a [test] Species")
p <- p + theme(plot.title=element_text(size=10))
p <- p + geom_line(data=data.frame(), aes(x=c(0,1), y=c(0,1)), colour="grey")
p <- p + annotate("text", x=0.50, y=0.00, hjust=0, vjust=0, size=5,
                  label=paste("AUC =", round(au, 2)))
print(p)

#### Calculate the area under the curve for the plot.

no.miss   <- na.omit(testing.Iris_N$Species)
miss.list <- attr(no.miss, "na.action")
attributes(no.miss) <- NULL

if (length(miss.list))
{
  pred_ksvm <- prediction(pr_ksvm_roc[-miss.list], no.miss)
} else
{
  pred_ksvm <- prediction(pr_ksvm_roc, no.miss)
}
performance(pred_ksvm, "auc")
```



